---
title: "R Notebook"
output: html_document
---

```{r}
#Install the packages

library(tidyverse)

```

###Q1.Reading the data into R in a tabular format, identifying, subsetting, and renaming the variables for your use

```{r}
raw = read.csv('raw_data.csv')
```

```{r}
#Remove rows with NA critic scores
data = raw %>% drop_na(Critic_Score)
head(data)

#Remove games with small number of critic count?

```

#### Identifying name and unit of variables:

xx_Sales are in millions.

###Q2. Forming the core data frame that you'll be working from by reshaping and summarizing the data, storing new data frames in memory where appropriate

```{r}
clean = read.csv('Cleaned Data 2.csv')
summary(clean)


#NEW LINE!
#The other New line!
```

###Q3. Cleaning the data according to your purpose for the dataset

```{r}



```

###Q4. Plotting distributions of your data

```{r}



```


###Q5. Calculating basic statistical metrics like central tendency measures

```{r}



```



###Q6. Some light correlational analysis/visualization of key variables.

```{r}



```


###Q7. A look forward to what further questions the analysis suggests and what it enables

```{r}



```





















